Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-12-01 response_round1.tex

        \[
         \widetilde{H}_{s,w + i}^{(k)} = \alpha_{0s}^{(k)} + 
                                          \alpha_{1s}^{(k)} 
                                          (\widetilde{ILI}_{s,w +i}^{(k)} \times P) + 
                                          \alpha_{2s}^{(k)} 
                                          (\widetilde{ILI}_{s,w +i}^{(k)} \times P)^2 + 
                                          \phi^{(k)} \widetilde{H}_{s,w + i - 1}^{(k)} + 
                                          \epsilon_{s,w + i}^{(k)}
        \]
        where $k \in \{1, ..., K\}$. The hospitalization draws were then combined into
        $\{H^{(k)}_{s,w + i}\}^K = (\widetilde{H}_{s,w + i}^{(1)}, ..., \widetilde{H}_{s,w + i}^{(K)})$,
        from which
        the probabilistic hospitalization forecast was estimated. In practice we set
        $K = 50,000$, and forecasts were obtained for weeks $i \in \{1, 2, 3, 4\}$.
        \\~\\
        \indent Occasionally $\{H^{(k)}_{s,w + i}\}^K$ included a small number of negative 
        values,
        which do not make sense when the distribution is meant to forecast
        hospitalizations, a nonnegative number. We attempted to alleviate this problem
        by modeling log-hospitalizations or by assuming hospitalizations followed a
        distribution truncated at 0, but these models led to poorer forecasts
        and issues drawing from the posterior distribution.
        For the forecast competition analysis in 
        section 5, all negative values of $\{H^{(k)}_{s,w + i}\}^K$ 
        were 
        set to 0 to reflect realistic values of hospitalizations and comply with the 
        FluSight forecasting rules.
        \\~\\

        \indent In the two-stage scheme, the posterior distribution of 
        model (1) parameters was not directly influenced by the 
        hospitalization data and the posterior distribution of model 
        (6) parameters was not directly influenced by model 
        (1) parameters. Hence there was limited feedback between the
        two components, but propagation of uncertainty in ILI forecasts was still 
        permitted in the estimating of hospitalization forecasts.
        This two-stage modeling is remeniscent of the Bayesian cut 
        described in \cite{plummer2015cuts} and \cite{nott2023bayesian}. Cutting a model
        into two component models or ``modules`` may be justified for several reasons
        including to reduce time to fit the model, avoiding mixing issues of posterior
        sampling distributions, improving predictive performance or to prevent
        model misspecification in one model to influence the other 
        \cite[]{nott2023bayesian, jacob2020unbiased, jacob2017better, 
        lee2017rigorous, plummer2015cuts}. A drawback
        from cutting a model is potential loss of useful information. 
        In our current 
        application for example, the ILI model parameters receive no potentially 
        useful information from hospiatlization data.
        \\~\\
        \indent The decision to cut the forecast model into two component models
        was made for three major reasons.
        When fitting the fully Bayesian joint model, the time to fit a single model 
        using
        MCMC sampling and
        obtain forecasts was sometimes many hours whereas fitting the two models
        separately took a fraction of the time. When assessing convergence of model
        parameters, it was rare that posterior sampling chains for the joint model
        showed convergence even after 55,000 iterations, whereas the component model 
        fits gave no signs which raised concern for convergence. And most importantly,
        the forecasts from the component models generally outperformed those of the 
        joint model in terms of minimizing proper scoring rules.
        \\~\\
  \end{quote}

\emph{In conclusion, I do think that the authors have done a good job of analysis and 
simulation based demonstrations of the results. These can be further improved 
by including some better measures of assessing prediction/forecasting accuracy, 
e.g. the CRPS (Continuous Ranked Probability Score), see for example Chapter 6 
of the book
``Bayesian modeling of spatio-temporal data with R`` by Sahu 
(Chapman and Hall, 2022).} 
\\~\\
In the simulation study in section 4 of the first version of this paper, 
scoring was
done using the CRPS, but in the FluSight analysis in section 5 scoring was done
using the WIS because the available forecasts are not amenable to being scored
the with the CRPS. A recommendation from one of the reviewers was to simplify 
by choosing one or the other scores, and we chose the WIS. To respond to this 
point, however, we modified the first paragraph on page 17. The paragraph is 
below and the added statements are bolded.

\begin{quote}

Model comparison was done by calculating a proper scoring rule for each 
forecast.
Proper scoring rules are the 
current standard for comparing performance between probabilistic forecasts 
and selecting the best forecasts according to the notion of maximizing 
sharpness subject to (auto-)calibration 
\cite[]{gneiting2007probabilistic, tsyplakov2013evaluation}. Proper scoring 
rules are commonly used in forecast comparison, and they are designed such 
that a 
forecaster is incentivized to be honest in the reporting of their forecasts 
\cite[]{gneiting2007strictly, gneiting2014probabilistic}.
\textbf{Commonly used proper scoring rules for continuous distribution forecasts
include the log score and the continuously
ranked probability score (CRPS).} 
The proper scoring rule primarily used in the FluSight competition and the 
COVID-19 Forecast Hub, and which is used in this simulation study,
is the negatively oriented
(smaller is better)
weighted interval score (WIS)
\cite[]{mathis2024evaluation, bracher2021evaluating}.
The WIS is used for scoring quantile or interval 
forecasts \textbf{--the forecast format used in both FluSight and the 
COVID-19 Forecast Hub--}
or forecasts made up of predicitive intervals of several nominal 
levels
\cite[]{gneiting2007strictly, gneiting2014probabilistic, bracher2021evaluating}. 
The WIS is 
defined in (8) where $Q$ is a forecast represented by all 
included quantiles, $B$ is the number of intervals,  $y^*$ is the observed 
value targeted by the forecast, $w_0 = 1/2$ and $w_b = \alpha_b / 2$ are 
weights for each interval, and $\alpha_b$ is the nominal level of the $b^{th}$ 
interval where $b \in \{1, ..., B\}$. 
$IS_{\alpha}$ is the interval score (IS), a proper scoring rule for a 
single interval, defined in (9). Here 
$\vmathbb{1}\{\cdot\}$ is the indicator function.
\textbf{We note that as the number of forecast intervals $B$ increases, the WIS becomes 
arbitrarily close to
the CRPS. Thus, forecast scores under the CRPS and the WIS should be similar
\cite[]{bracher2021evaluating}.}
\end{quote}

### 2025-12-01 response_round1.tex

\Huge
\noindent AE1
\normalsize
\\~\\

% \emph{
% I think the authors did a great job in this newly submitted version and 
% addressed most of the earlier raised comments in a nice and convincing way. 
% The paper is well written and interesting to read. 
% }
% I only have two remaining comments.

\begin{enumerate}[-]

  \item \emph{Section 3.7. End of of first paragraph: ``..., but propagation of 
  uncertainty   in ILI forecasts was still permitted in the estimating of 
  hospitalisation forecasts.``
  }
  \emph{
  Please clarify more explicitly how uncertainty was propagated between the two 
  model components. My understanding is that this was achieved by incorporating 
  not only point estimates of the parameters but also samples from the predictive 
  distribution of the ILI model. If this is correct, please state it clearly 
  already at this stage and consider adding a brief discussion of the advantages 
  and disadvantages of this approach.}
  \\~\\
  To clarify how uncertainty was propogated, we consolidated sections
  3.7 and 3.8, reordered the main ideas, and removed redundant information. We
  also added some advantages/disadvantages of our approach. The changes now
  read:
  \begin{quote}
        \subsection*{3.7 Hospitalization Forecasts Using the Bayesian Cut}
        \label{sec:implementation_posterior}

### 2025-12-03 response_round1.tex

% \emph{
% I think the authors did a great job in this newly submitted version and 
% addressed most of the earlier raised comments in a nice and convincing way. 
% The paper is well written and interesting to read. 
% }
% I only have two remaining comments.

\begin{enumerate}[-]

  \item \emph{Section 3.7. End of of first paragraph: ``..., but propagation of 
  uncertainty   in ILI forecasts was still permitted in the estimating of 
  hospitalisation forecasts.``
  }
  \emph{
  Please clarify more explicitly how uncertainty was propagated between the two 
  model components. My understanding is that this was achieved by incorporating 
  not only point estimates of the parameters but also samples from the predictive 
  distribution of the ILI model. If this is correct, please state it clearly 
  already at this stage and consider adding a brief discussion of the advantages 
  and disadvantages of this approach.}
  \\~\\
  To clarify how uncertainty was propogated, we consolidated sections
  3.7 and 3.8, reordered the main ideas, and removed redundant information. We
  also added some advantages/disadvantages of our approach. The changes now
  read:
  \begin{quote}
        \subsection*{3.7 Hospitalization Forecasts Using the Bayesian Cut}
        \label{sec:implementation_posterior}

        Rather than combine the ILI and hopsitalization models into a single model,
        the ILI model (1) and hospitalization model
        (6) were fit separately via Bayesian posterior updating 
        in two stages and then fused together to produce hospitalization 
        forecasts. In the first stage, future ILI 
        forecasts were obtained from the ILI forecast model in (7).
        Here 
        $p(\xi | \textbf{ILI}_w)$ 
        is posterior distribution from the ILI model (1)
        and $\textbf{ILI}_w$ represents all observed ILI data up to week $w$.
        The ILI forecast model was obtained by integrating over the 
        parameters 
        $\xi = (\pi$, $\kappa$, $\sigma^2_{\gamma}$, $\sigma^2_{\gamma_W})$.
        The desired forecasts are for weeks $w + i$ 
        where $i$ is a positive integer, and $\widetilde{ILI}_{w + i}$ represents the 
        predicted or forecasted ILI at $i$ weeks in the future.
        Note that
        in this section
        the parameter subscript for season $s$ is dropped to simplify notation.

        % \begin{equation}
        %     \label{eq:ili_post}
        %     p(\widetilde{ILI}_{s,w +i} | \textbf{ILI}_w) = \int \int \int \int 
        %     p(\widetilde{ILI}_{s,w + i} | \boldsymbol{\pi}_s, \kappa_s, 
        %     \sigma^2_{\gamma}, \sigma^2_{\gamma_W}) p(\boldsymbol{\pi}_s, \kappa_s, 
        %     \sigma^2_{\gamma}, \sigma^2_{\gamma_W} | \textbf{ILI}_w) 
        %     d\boldsymbol{\pi}_s d \kappa_s d \sigma^2_{\gamma} d \sigma^2_{\gamma_W}
        % \end{equation}

        \begin{equation}
        \tag{7}
            \label{eq:ili_post}
            p(\widetilde{ILI}_{w +i} | \textbf{ILI}_w) = \int  
            p(\widetilde{ILI}_{w + i} | \xi) 
            p(\xi | \textbf{ILI}_w) 
            d\xi
        \end{equation}
        % \jarad{It doesn't make sense to have 4 $\int$ here since $\pi_s$ is a vector.}
        % \spencer{Isn't that captured in $d \pi_s$?}

        In the second stage, the posterior distribution
        for parameters of the hospitalization 
        model (6) given observed
        hospitalization data $\textbf{H}_w$ and $\textbf{ILI}_w$ was obtained.
        The posterior distribution is denoted as
        $p(\psi | \textbf{H}_w, \textbf{ILI}_w)$.
        The ILI forecast model in (7) was then combined with 
        the hospitalization posterior distribution
        to produce a hospitalization forecast $\widetilde{H}_{w + i}$ 
        for week $w + i$.
        Both the ILI forecast model in (7) and the hospitalization
        posterior distributions were estimated via Markov chain Monte Carlo 
        (MCMC) sampling.
        In the first or ILI stage, $K$ MCMC draws
        $(\widetilde{ILI}_{w +i}^{(1)}, ..., \widetilde{ILI}_{w +i}^{(K)})$
        from the forecast model were produced,
        and in the second or hospitalization stage
        $K$ draws $(\psi^{(1)}, ..., \psi^{(K)})$ 
        from the hospitalization posterior 
        were produced. Each of the
        ILI forecast and hospitalization draws was then plugged into 
        the hospitalization model
        (6) to produce the approximate hospitalization forecast
        distribution in the bottom line of(8). 
        Here $k \in \{1, ..., K\}$, 
        and forecasts were obtained for weeks $i \in \{1, 2, 3, 4\}$.
        In the analyses in sections \ref{sec:simulation2} and \ref{sec:analysis}
        we set $K = 50,000$ draws.

        \begin{equation}
        \tag{8}
        \begin{aligned}
        \label{eq:hosp_post_pred}
          &p(\widetilde{H}_{w + i} | \textbf{H}_w, \textbf{ILI}_w)\\
          &= \int p(\widetilde{H}_{w +i} | 
               \psi, \widetilde{ILI}_{w +i}, \textbf{H}_w)
               p(\psi | \textbf{H}_w, \textbf{ILI}_w) d \psi d\widetilde{ILI} \\
          &\approx \frac{1}{K} p(\widetilde{H}_{w + i}^{(k)} | \psi^{(k)},  
                              \tilde{ILI}_{w +i}^{(k)}, \textbf{H}_w, \textbf{ILI}_w) 
        \end{aligned}
        \end{equation}
        % \[
        %  \widetilde{H}_{s,w + i}^{(k)} = \alpha_{0s}^{(k)} + 
        %                                   \alpha_{1s}^{(k)} 
        %                                   (\widetilde{ILI}_{s,w +i}^{(k)} \times P) + 
        %                                   \alpha_{2s}^{(k)} 
        %                                   (\widetilde{ILI}_{s,w +i}^{(k)} \times P)^2 + 
        %                                   \phi^{(k)} \widetilde{H}_{s,w + i - 1}^{(k)} + 
        %                                   \epsilon_{s,w + i}^{(k)}
        % \]
        % where $k \in \{1, ..., K\}$. 
        % The hospitalization draws were then combined into
        % $\{H^{(k)}_{s,w + i}\}^K = (\widetilde{H}_{s,w + i}^{(1)}, ..., \widetilde{H}_{s,w + i}^{(K)})$,
        % from which
        % the probabilistic hospitalization forecast was estimated.
        % In practice we set
        % $K = 50,000$, and forecasts were obtained for weeks $i \in \{1, 2, 3, 4\}$.

        % \[ \begin{array}{rl}
        % p(\tilde{H}_w | H_w, ILI_w) 
        % &=               \int p(\tilde{H}_w | \tilde{ILI}_w, H_w) p (\tilde{ILI}_w | H_w, ILI_w)  d\tilde{ILI}_w \\
        % &\approx  \int p(\tilde{H}_w | \tilde{ILI}_w, H_w) p (\tilde{ILI}_w | ILI_w)  d\tilde{ILI}_w
        % \end{array} \]

        In the two-stage scheme, the posterior distribution of the ILI
        model (1) parameters was not directly influenced by the 
        hospitalization data and the posterior distribution of the hospitalization model 
        (6) was not directly influenced by ILI model 
        parameters. Hence there was limited feedback between the
        two components, but the propagation of uncertainty in ILI forecasts was still 
        accomplished in the estimating of hospitalization forecasts through
        the forecast model (8).
        This two-stage modeling is reminiscent of the Bayesian cut 
        described in \cite{plummer2015cuts} and \cite{nott2023bayesian}. Cutting a model
        into two component models or ``modules'' may be justified for several reasons
        including to reduce time to fit the model, avoiding mixing issues of posterior
        sampling distributions, improving predictive performance or to prevent
        model misspecification in one model to influence the other 
        \cite[]{nott2023bayesian, jacob2020unbiased, jacob2017better, 
        lee2017rigorous, plummer2015cuts}. A drawback
        from cutting a model is potential loss of useful information. 
        In our current 
        application for example, the ILI model parameters receive no potentially 
        useful information from hospiatlization data.

        The decision to cut the forecast model into two component models
        was made for three major reasons.
        When fitting the fully Bayesian joint model, the time to fit a single model 
        using
        MCMC sampling and
        obtain forecasts was sometimes many hours whereas fitting the two models
        separately took a fraction of the time. When assessing convergence of model
        parameters, it was rare that posterior sampling chains for the joint model
        showed convergence even after 55,000 iterations, whereas the component model 
        fits gave no signs which raised concern for convergence. And most importantly,
        the forecasts from the component models generally outperformed those of the 
        joint model in terms of minimizing proper scoring rules.
        \\~\\
  \end{quote}
  \emph{
  \item I recommend including the statement raised by the reviewer in the first 
  submission—that WIS approximates CRPS (ideally supported with a reference)—and 
  therefore leads to essentially the same conclusions. I think the motivation for 
  using WIS instead of CRPS is well explained, especially given that WIS is the 
  primary evaluation measure used in the FluSight competition} 
  \\~\\

@@

% In spite of the above criticisms, 
\emph{I appreciate the hierarchical modeling 
approach of fitting the two models separately in components. But I wonder how 
the uncertainty has been propagated from one component model to another. 
Cutting the feedback idea is well understood but one still needs to integrate 
uncertainty to get an overall measure of the uncertainty in the forecasts. 
I did not clearly understand this issue from my reading of  the paper. I can 
suggest one way to propagate this uncertainty is by using MCMC samples 
(and methods), see for example, the paper,  ``A rigorous statistical framework 
for spatio-temporal pollution prediction and estimation of its long-term impact 
on health`` by 
D Lee, S Mukhopadhyay, A Rushworth, and SK Sahu, in Biostatistics (2017).}
\\~\\
We appreciated this comment and the included reference. We used the reference
to assist in our new explanation, and made sure to cite it. 
To clarify how uncertainty was propogated, we consildated sections
  3.7 and 3.8, reordered the main ideas, and removed redundant information. We
  also added some advantages/disadvantages of our approach. The changes now
  read:
  \begin{quote}
        \subsection*{3.7 Hospitalization Forecasts Using the Bayesian Cut}
        \label{sec:implementation_posterior}

        Rather than combine the ILI and hopsitalization models into a single model,
        the ILI model (1) and hospitalization model
        (6) were fit separately via Bayesian posterior updating 
        in two stages and then fused together to produce hospitalization 
        forecasts. In the first stage, future ILI 
        forecasts were obtained from the ILI forecast model in (7).
        Here 
        $p(\xi | \textbf{ILI}_w)$ 
        is posterior distribution from the ILI model (1)
        and $\textbf{ILI}_w$ represents all observed ILI data up to week $w$.
        The ILI forecast model was obtained by integrating over the 
        parameters 
        $\xi = (\pi$, $\kappa$, $\sigma^2_{\gamma}$, $\sigma^2_{\gamma_W})$.
        The desired forecasts are for weeks $w + i$ 
        where $i$ is a positive integer, and $\widetilde{ILI}_{w + i}$ represents the 
        predicted or forecasted ILI at $i$ weeks in the future.
        Note that
        in this section
        the parameter subscript for season $s$ is dropped to simplify notation.

        % \begin{equation}
        %     \label{eq:ili_post}
        %     p(\widetilde{ILI}_{s,w +i} | \textbf{ILI}_w) = \int \int \int \int 
        %     p(\widetilde{ILI}_{s,w + i} | \boldsymbol{\pi}_s, \kappa_s, 
        %     \sigma^2_{\gamma}, \sigma^2_{\gamma_W}) p(\boldsymbol{\pi}_s, \kappa_s, 
        %     \sigma^2_{\gamma}, \sigma^2_{\gamma_W} | \textbf{ILI}_w) 
        %     d\boldsymbol{\pi}_s d \kappa_s d \sigma^2_{\gamma} d \sigma^2_{\gamma_W}
        % \end{equation}

        \begin{equation}
        \tag{7}
            \label{eq:ili_post}
            p(\widetilde{ILI}_{w +i} | \textbf{ILI}_w) = \int  
            p(\widetilde{ILI}_{w + i} | \xi) 
            p(\xi | \textbf{ILI}_w) 
            d\xi
        \end{equation}
        % \jarad{It doesn't make sense to have 4 $\int$ here since $\pi_s$ is a vector.}
        % \spencer{Isn't that captured in $d \pi_s$?}

        In the second stage, the posterior distribution
        for parameters of the hospitalization 
        model (6) given observed
        hospitalization data $\textbf{H}_w$ and $\textbf{ILI}_w$ was obtained.
        The posterior distribution is denoted as
        $p(\psi | \textbf{H}_w, \textbf{ILI}_w)$.
        The ILI forecast model in (7) was then combined with 
        the hospitalization posterior distribution
        to produce a hospitalization forecast $\widetilde{H}_{w + i}$ 
        for week $w + i$.
        Both the ILI forecast model in (7) and the hospitalization
        posterior distributions were estimated via Markov chain Monte Carlo 
        (MCMC) sampling.
        In the first or ILI stage, $K$ MCMC draws
        $(\widetilde{ILI}_{w +i}^{(1)}, ..., \widetilde{ILI}_{w +i}^{(K)})$
        from the forecast model were produced,
        and in the second or hospitalization stage
        $K$ draws $(\psi^{(1)}, ..., \psi^{(K)})$ 
        from the hospitalization posterior 
        were produced. Each of the
        ILI forecast and hospitalization draws was then plugged into 
        the hospitalization model
        (6) to produce the approximate hospitalization forecast
        distribution in the bottom line of(8). 
        Here $k \in \{1, ..., K\}$, 
        and forecasts were obtained for weeks $i \in \{1, 2, 3, 4\}$.
        In the analyses in sections \ref{sec:simulation2} and \ref{sec:analysis}
        we set $K = 50,000$ draws.

        \begin{equation}
        \tag{8}
        \begin{aligned}
        \label{eq:hosp_post_pred}
          &p(\widetilde{H}_{w + i} | \textbf{H}_w, \textbf{ILI}_w)\\
          &= \int p(\widetilde{H}_{w +i} | 
               \psi, \widetilde{ILI}_{w +i}, \textbf{H}_w)
               p(\psi | \textbf{H}_w, \textbf{ILI}_w) d \psi d\widetilde{ILI} \\
          &\approx \frac{1}{K} p(\widetilde{H}_{w + i}^{(k)} | \psi^{(k)},  
                              \tilde{ILI}_{w +i}^{(k)}, \textbf{H}_w, \textbf{ILI}_w) 
        \end{aligned}
        \end{equation}
        % \[
        %  \widetilde{H}_{s,w + i}^{(k)} = \alpha_{0s}^{(k)} + 
        %                                   \alpha_{1s}^{(k)} 
        %                                   (\widetilde{ILI}_{s,w +i}^{(k)} \times P) + 
        %                                   \alpha_{2s}^{(k)} 
        %                                   (\widetilde{ILI}_{s,w +i}^{(k)} \times P)^2 + 
        %                                   \phi^{(k)} \widetilde{H}_{s,w + i - 1}^{(k)} + 
        %                                   \epsilon_{s,w + i}^{(k)}
        % \]
        % where $k \in \{1, ..., K\}$. 
        % The hospitalization draws were then combined into
        % $\{H^{(k)}_{s,w + i}\}^K = (\widetilde{H}_{s,w + i}^{(1)}, ..., \widetilde{H}_{s,w + i}^{(K)})$,
        % from which
        % the probabilistic hospitalization forecast was estimated.
        % In practice we set
        % $K = 50,000$, and forecasts were obtained for weeks $i \in \{1, 2, 3, 4\}$.

        % \[ \begin{array}{rl}
        % p(\tilde{H}_w | H_w, ILI_w) 
        % &=               \int p(\tilde{H}_w | \tilde{ILI}_w, H_w) p (\tilde{ILI}_w | H_w, ILI_w)  d\tilde{ILI}_w \\
        % &\approx  \int p(\tilde{H}_w | \tilde{ILI}_w, H_w) p (\tilde{ILI}_w | ILI_w)  d\tilde{ILI}_w
        % \end{array} \]

        In the two-stage scheme, the posterior distribution of the ILI
        model (1) parameters was not directly influenced by the 
        hospitalization data and the posterior distribution of the hospitalization model 
        (6) was not directly influenced by ILI model 
        parameters. Hence there was limited feedback between the
        two components, but the propagation of uncertainty in ILI forecasts was still 
        accomplished in the estimating of hospitalization forecasts through
        the forecast model (8).
        This two-stage modeling is reminiscent of the Bayesian cut 
        described in \cite{plummer2015cuts} and \cite{nott2023bayesian}. Cutting a model
        into two component models or ``modules'' may be justified for several reasons
        including to reduce time to fit the model, avoiding mixing issues of posterior
        sampling distributions, improving predictive performance or to prevent
        model misspecification in one model to influence the other 
        \cite[]{nott2023bayesian, jacob2020unbiased, jacob2017better, 
        lee2017rigorous, plummer2015cuts}. A drawback
        from cutting a model is potential loss of useful information. 
        In our current 
        application for example, the ILI model parameters receive no potentially 
        useful information from hospiatlization data.

        The decision to cut the forecast model into two component models
        was made for three major reasons.
        When fitting the fully Bayesian joint model, the time to fit a single model 
        using
        MCMC sampling and
        obtain forecasts was sometimes many hours whereas fitting the two models
        separately took a fraction of the time. When assessing convergence of model
        parameters, it was rare that posterior sampling chains for the joint model
        showed convergence even after 55,000 iterations, whereas the component model 
        fits gave no signs which raised concern for convergence. And most importantly,
        the forecasts from the component models generally outperformed those of the 
        joint model in terms of minimizing proper scoring rules.
        \\~\\
  \end{quote}
